### 2024-06-25 conteudo/introduction/intro.tex
Add update of intro, 24/06

The Linux kernel is a major project in the open source community, containing more then 19 million lines of code and more
then thirteen thousand contributors along the lifespan of the project \citep{linuxquantity}. Given the magnitude of the project,
it is unrealistic to expect that all contributors followed the best programming practices and principles throughout every 
contributions they made to the project. It is expected to find a good amount of bad quality code artifacts in the source code, 
which could result in hindering or compromising the maintenance of this project, as well as the indication of new features for it.

@@

Since our searches for solution to the AMD Display driver problem with duplicated code became fruitless. We propose to create a tool
that approaches the given problem and can be adapted with a moderated amount of effort to support other open source projects facing
similar issues. Given our proposed tool, we desire to validate if it is capable of detecting duplicated code and if the tool 
is in fact useful to mitigate the AMD Display driver problem with duplicated code.

>>>>

Representing 3.77\% of the personal desktops and 70,69\% of the smartphones worldwide, the Linux kernel 
is a open source project providing value to billions of people in their daily lives. 
The magnitude that the project has reached over the years makes the addition of features, as well as handling bugs and security 
vunerabilities, potentially affect a significant number of people, demonstrating the importance of maintaining the 
kernel.

The maintainment of the Linux kernel is a complex task, as the project contains more then 19 million lines of code and have more
then thirteen thousand contributors along the lifespan of the project \citep{linuxquantity}. Given the magnitude of the project,
it is unrealistic to expect that all contributors followed the best programming practices and principles throughout every 
contributions they made to the project. It is expected to find a good amount of bad quality code artifacts in the source code, 
which could result in hindering or compromising the maintenance of this project, as well as the addition of new features for it.

@@

Since our searches for solutions to the duplicated code problem become fruitless. We
intend to propose an approach to indentify and mitigate the code duplications in the Linux Kernel. For that, 
we propose a tool capable to indentify code duplications in the kernel, and by participant observation analyse and mitigate the 
code duplications found while cataloging the software engineer methods used in process such as refactoring methods.

An additional usefulness of our proposed approach is to give a new method to people become contributors to the Linux kernel. The 
process of starting to contribute to the Linux kernel can be unintuitive, which can cause people to distance themselves.
Our approach provides to the community a new form of newcomers to start contributing by removing simple code duplications, 
while they learn the whole process of being a Linux contribuitor.
